---
title: "Beer Production"
author: "Maggie Suero"
date: "3/31/2020"
---

```{r}
library(tidyverse)
library(geojsonio)
library(rgdal)
library(broom) # tidy spdf
library(rgeos) # calculate the centroid of each hexagon to add the label
library(maps)
library(mapproj)
library(viridis)
library(viridisLite)
library(scales)
```
Data base from the Alcohol and Tobacco Tax and Trade Bureau (TTB)

```{r}
# Import the data
brewing_materials <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-03-31/brewing_materials.csv')
beer_taxed <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-03-31/beer_taxed.csv')
brewer_size <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-03-31/brewer_size.csv')
beer_states <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-03-31/beer_states.csv')
```

Create the Hex 
```{r}
# Download the Hex boundaries at geojson format from: https://team.carto.com/u/andrew/tables/andrew.us_states_hexgrid/public/map

# Load the Hex boundaries into the Spatial Polygons Data Frama
spdf <- geojson_read("DATA/us_states_hexgrid.geojson",  what = "sp")

# Reformating the data
spdf@data = spdf@data %>%
  mutate(google_name = gsub(" \\(United States\\)", "", google_name))

# Fortify into a data frame format to be shown with ggplot2
spdf_fortified <- tidy(spdf, region = "iso3166_2")

# Calculate the centroid of each hexagon to add the label:
centers <- cbind.data.frame(data.frame(gCentroid(spdf, byid=TRUE), id=spdf@data$iso3166_2))

# Show it
plot(spdf)
```
Add State name

```{r}
# Merge geospatial and numerical information
data <- spdf_fortified %>%
  left_join(beer_states,  by=c("id"="state")) %>%
  filter(year == "2019", type == "Bottles and Cans") %>% 
  mutate(Barrels = round(barrels, digits = 0))
```
Basic Hex plot

```{r}
# Plot
state_name <- spdf_fortified %>% 
  ggplot() +
  geom_polygon(data = data, aes(x = long, y = lat, group = group), fill="lavender", color="black") +
  geom_text(data=centers, aes(x=x, y=y, label=id)) +
  theme_void() +
  coord_map()

plot(state_name)
```
Customized hexbin choropleth map

```{r}
ggplot() +
  geom_polygon(data = data, aes(x = long, y = lat, fill =  Barrels, group = group), size=0, alpha=0.95, color="black") +
  geom_text(data=centers, aes(x=x, y=y, label=id), color="brown", fontface = "bold") +
  scale_x_continuous(labels = comma) +
  labs(title = "Beer production by State", 
       subtitle = "Bottles and Cans in 2019",
       caption = "Visualization by @G33kyCats") +
  theme_void() +
  theme(plot.title = element_text(face = "bold", hjust = 0.5, size = 20),
        plot.subtitle = element_text(hjust = 0.5, size = 16),
        plot.caption = element_text(face = "italic", size = 11, colour = "grey50"))+
  #viridis direction: 1 colors are ordered from darkest to lightest, -1 the order is reversed
  #viridis colormaps: "magma" (or "A"), "inferno" ("B"), "plasma" ("C"), "viridis" ("D"), and "cividis" ("E") 
  scale_fill_viridis_c(begin = 0.53, end = 1, option = "inferno", direction = 1, trans = "log", na.value = NA) +
  coord_map()
```

Another Customized Hexbin Choropleth Map
```{r}

kegs <- spdf_fortified %>%
  left_join(beer_states,  by=c("id"="state")) %>%
  filter(year == "2019", type == "Kegs and Barrels") %>% 
  mutate(Barrels = round(barrels, digits = 0))

ggplot() +
  geom_polygon(data = kegs, aes(x = long, y = lat, fill =  barrels, group = group), size=0, alpha=0.8, color="brown") +
  geom_text(data=centers, aes(x=x, y=y, label=id), color="brown", fontface = "bold") +
  scale_x_continuous(labels = comma) +
  labs(title = "Beer production by State", 
       subtitle = "Kegs and Barrels in 2019",
       caption = "Visualization by @G33kyCats") +
  theme_void() +
  theme(plot.title = element_text(face = "bold", hjust = 0.5, size = 20),
        plot.subtitle = element_text(hjust = 0.5, size = 16),
        plot.caption = element_text(face = "italic", size = 11, colour = "grey50")) +
  scale_fill_viridis_c(option = "inferno", direction = -1, trans = "log", na.value = NA) +
  coord_map()

  
```

This week on Tidy Tuesday I learned how to merge geospatial and numerical information, in other words, how to map the data. I found very useful this site: https://www.r-graph-gallery.com/328-hexbin-map-of-the-usa.html where you have a step by step process.
I also learned how to use the viridis library (or at least part of it). 
